The ChEMBL database as Linked Open Data

### 2012-07-21 article.tex
Updated with a working SPARQL

The following SPARQL query identifies a set of molecules, which based on data curated from the 
literature and stored in the ChEMBL-RDF data model, selectively bind Human Cyclin-Dependent Kinase 2 
(UniProt: P24941) over Human Cyclin-Dependent Kinase 4 (UniProt: P11802).

NOTE: Query should return 65 molecules

\begin{small}
\begin{verbatim}
select distinct ?molecule WHERE 
{ 
  ?assay ?p chembl:Assay ;
  chembl:hasTarget ?target .
  ?activity ?p chembl:Activity ;
  chembl:forMolecule ?molecule ;
  chembl:onAssay ?assay ;
  chembl:type ?type ;
  chembl:standardUnits ?unit ;
  chembl:standardValue ?value;
  chembl:relation ?relation
  FILTER (
    ?type = "IC50"  &&
    ?unit = "nM"    &&
    ?value  < 50    &&
    ?relation = "="
  ) .
  ?target ?p chembl:Target;
  dc:identifier ?id
  FILTER (
    ?id = "uniprot:P24941"
  ) .
  { 
    select ?molecule WHERE 
    {
      ?assay ?p chembl:Assay ;
      chembl:hasTarget ?target .
      ?activity ?p chembl:Activity ;
      chembl:forMolecule ?molecule ;
      chembl:onAssay ?assay;
      chembl:type ?type ;
      chembl:standardUnits ?unit ;
      chembl:standardValue ?value ;
      chembl:relation ?relation
      FILTER (
        ?type = "IC50"  &&
        ?unit = "nM"    &&
        ?value  > 200   &&
        ?relation = "="
      ) .
      ?target ?p chembl:Target;
      dc:identifier ?id
      FILTER (
        ?id = "uniprot:P11802"
      ) .
    }
  }
}
\end{verbatim}
\end{small}

>>>>

The following SPARQL query identifies a set of 65 molecules, which based on data curated from the 
literature and stored in the ChEMBL-RDF data model, selectively bind Human Cyclin-Dependent Kinase 2 
(UniProt: P24941) over Human Cyclin-Dependent Kinase 4 (UniProt: P11802).

\begin{small}
\begin{verbatim}
select distinct ?molecule WHERE {
  ?target1 owl:sameAs <http://bio2rdf.org/uniprot:P24941> .
  ?assay1 chembl:hasTarget ?target1 .
  ?activity1 chembl:onAssay ?assay1 ;
    chembl:forMolecule ?molecule ;
    chembl:type "IC50" ;
    chembl:standardUnits "nM" ;
    chembl:standardValue ?value1 ;
    chembl:relation "="
    FILTER ( ?value1 < 50 ) .
  ?target2 owl:sameAs <http://bio2rdf.org/uniprot:P11802> .
  ?assay2 chembl:hasTarget ?target2 .
  ?activity2 chembl:onAssay ?assay2 ;
    chembl:forMolecule ?molecule ;
    chembl:type "IC50" ;
    chembl:standardUnits "nM" ;
    chembl:standardValue ?value2 ;
    chembl:relation "="
    FILTER ( ?value2 > 200 ) .
}
\end{verbatim}
\end{small}
